---
title: "Lab 10 - Last One Ever"
author: "Meghna Rao"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(beepr)
library(tidyverse)
library(praise)
library(cowsay)
library(sf)
library(paletteer)
library(janitor)
library(usethis)
```


## Beepr beeps

you can have r code that takes days to run. you might like to have a sound go off when the code is done running. 
Use `beep()` to give yourself an audio alert. Test the sound in the console

## for loop + beep

for loop is usually functions built in that do it for you.

```{r, eval = FALSE}
# want to create a sequence that goes from 1 - 99 and reverse reverse
# rev wraps it in a reverse function rev
# for each element i in this sequence rev(seq(1:99))
# paste function puts things together in more than a string
for (i in rev(seq(1:9999))) {
  print(paste(i, "bottles of beer on the wall")) # print(i) just prints the numbers and paste will put in the element
  
}

beep(21)
```

## Praise - positive messages only

`praise()` to specify template pieces that will be randomly selected `${}` and squiggly blankets needs a gramatical phrase that praise recognizes

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!")

beep(99)
```

```{r}
say("I love tacos!", by = "trilobite", what_color = "blue", by_color = "yellow")
```

## usethis for everything

used to store personal access token and for initial set up
allison's fav package
here to make our lives easier

`usethis::edit_r_profile()` in the console


R Project firs, then git & GitHub (not code you would run every single time)

- usethis::use_git() # makes version controlle local repo
- usethis::use_github() # makes the repo in github.

## Paletteer: aggregated color palattes

lots of color palattes to do things in R
discrete color palattes. 
`view(palettes_d_names)


```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("taylor::taylorSwift") # we are doing a discrete variable for storm names
```
`paletteer_d()`

## Map of Jornada LTER Vegetation

geometries are sticky, it assumes that we want to maintain spatial associations amongst observations

so we can apply tools for data wrangling to spatial data

`read_sf`

```{r}
jornada_veg <- read_sf("doc.kml") %>% 
  select(Name) %>% 
  clean_names()

ggplot(data = jornada_veg) +
  geom_sf(data = jornada_veg, aes(fill = name)) +
  theme_minimal() +
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jornada basin LTER Vegetation", legend.title = "Name")

# update this map so each vegetation type has a different fill color
# update the theme
# customize the color palette

ggsave(filename = "my_awesome_jornada_map.png", width = 8, height = 5)
```



